article title

### 2022-07-19 article.tex
Tidy tables, correct kappa miniscule

\begin{table}[H]
\begin{flushleft}
\begin{tabular}{lcccc}
\toprule
letter & code & miniscule & code & majuscule \\
\midrule
alpha   & 03b1 & α & 0391 & Α \\
beta    & 03b2 & β & 0392 & Β \\
gamma   & 03b3 & γ & 0393 & Γ \\
delta   & 03b4 & δ & 0394 & Δ \\
epsilon & 03b5 & ε & 0395 & Ε \\
zeta    & 03b6 & ζ & 0396 & Ζ \\
eta     & 03b7 & η & 0397 & Η \\
theta   & 03b8 & θ & 0398 & Θ \\
iota    & 03b9 & ι & 0399 & Ι \\
kappa   & 03b1 & α & 039a & Κ \\
lambda  & 03bb & λ & 039b & Λ \\
mu      & 03bc & μ & 039c & Μ \\
nu      & 03bd & ν & 039d & Ν \\
xi      & 03be & ξ & 039e & Ξ \\
omicron &      & o &      & O \\
pi      & 03c0 & π & 03ao & Π \\
rho     & 03c1 & ρ & 03a1 & Ρ \\
sigma   & 03c3 & σ & 03a3 & Σ \\
tau     & 03c4 & τ & 03a4 & Τ \\
upsilon & 03c5 & υ & 03a5 & Υ \\
phi     & 03c6 & φ & 03a6 & Φ \\
chi     & 03c7 & χ & 03a7 & Χ \\
psi     & 03c8 & ψ & 03a8 & Ψ \\
omega   & 03c9 & ω & 03a9 & Ω \\
\bottomrule
\end{tabular}
\label{tab:greek_unicode}
\caption{Greek Unicode}
\end{flushleft}
\end{table}

>>>>

\begin{table}[H]
\begin{flushleft}
\begin{tabular}{lcccc}
\toprule
letter & code & miniscule & code & majuscule \\
\midrule
alpha   & 03b1 & α & 0391 & Α \\
beta    & 03b2 & β & 0392 & Β \\
gamma   & 03b3 & γ & 0393 & Γ \\
delta   & 03b4 & δ & 0394 & Δ \\
epsilon & 03b5 & ε & 0395 & Ε \\
zeta    & 03b6 & ζ & 0396 & Ζ \\
eta     & 03b7 & η & 0397 & Η \\
theta   & 03b8 & θ & 0398 & Θ \\
iota    & 03b9 & ι & 0399 & Ι \\
kappa   & 03ba & κ & 039a & Κ \\
lambda  & 03bb & λ & 039b & Λ \\
mu      & 03bc & μ & 039c & Μ \\
nu      & 03bd & ν & 039d & Ν \\
xi      & 03be & ξ & 039e & Ξ \\
omicron &      & o &      & O \\
pi      & 03c0 & π & 03ao & Π \\
rho     & 03c1 & ρ & 03a1 & Ρ \\
sigma   & 03c3 & σ & 03a3 & Σ \\
tau     & 03c4 & τ & 03a4 & Τ \\
upsilon & 03c5 & υ & 03a5 & Υ \\
phi     & 03c6 & φ & 03a6 & Φ \\
chi     & 03c7 & χ & 03a7 & Χ \\
psi     & 03c8 & ψ & 03a8 & Ψ \\
omega   & 03c9 & ω & 03a9 & Ω \\
\bottomrule
\end{tabular}
\label{tab:greek_unicode}
\caption{Greek Unicode}
\end{flushleft}
\end{table}
